Verifying Demonstrations

### 2018-06-01 paper/DB-anon-cred.tex

One protocol exists in the literature that provides \acp{PPK} with all the 
desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
  shorter notation.}.
However, ProProx provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.

@@

The protocol is \ac{DBTF}-resistant, indeed if the malicious prover gives both responses to the adversary, the adversary can compute his secret key.
This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can extract the secret.
The protocol is also secure against distance hijacking due to the fact that it is the authenticated bitstring that is used during the \ac{DB} phase, not the challenge bit string as in the protocol of Brands-Chaum.

>>>>

One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
However, ProProx is not secure against a malicious verifier and does not provide \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.

@@

The protocol is \ac{DBTF}-resistant, indeed if the malicious prover gives both responses to the adversary, the adversary can compute his secret key.
This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can leak the secret.
The protocol is also secure against distance hijacking due to the fact that it is the authenticated bitstring that is used during the \ac{DB} phase, not the challenge bitstring as in the protocol of Brands-Chaum.

### 2018-06-01 paper/DistanceBounding.tex
Removes Seb's comment that has been fixed

\subsection{Distance bounding}%
\label{DistanceBounding}

@@

The main attacks against \ac{DB} protocols can be summarized as follows:
%Seb: the following names of attacks should all have the first letters in capital
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
%Seb: the two following properties should be defined more precisely
  \item \Acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against this verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PKE} for discrete logarithms).

>>>>

\subsection{Distance-bounding protocols}%
\label{DistanceBounding}

@@

The main attacks against \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
%Seb: the two following properties should be defined more precisely
  \item \Acf{DBDH}: similar to \ac{DBDF} but using the presence of an honest prover close to the verifier.
  \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PKE} for discrete logarithms).

### 2018-06-01 paper/TimeStamp.tex

%\NewScheme{\TS}{TS}
\NewAlgorithm{\TSget}{\TS.\!Get}
\NewAlgorithm{\TSstamp}{\TS.\!Stamp}
\NewAlgorithm{\TSverify}{\TS.\!Verify}
\NewAlgorithm{\TStime}{\TS.\!Time}

@@

We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and 
return the identifier of the block into which \(x\) was included.
\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted transactions and usually some randomness (\eg nonces and miners' secrets).
The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
Having a dedicated blockchain for a protest will not do, and thus it is better 
to use a blockchain which is used for other things too.

There are some additional properties that we need from \(\TS\), which are implied by blockchains.
First, we need \emph{immutability}, to ensure that once we commit something (through \(\TSstamp\)) it will remain there.
We will use this to ensure verifiability as the data must remain to be verifiable.
Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
For instance using blockchains, we can store the hash of the block in which our 
data was committed, while this block remains we are sure that our data remains 
committed --- even if we no longer remember what our data looked like.

>>>>

\NewScheme{\TS}{TS}
\NewAlgorithm{\TSget}{\TS.\!Get}
\NewAlgorithm{\TSstamp}{\TS.\!Stamp}
\NewAlgorithm{\TSverify}{\TS.\!Verify}
\NewAlgorithm{\TStime}{\TS.\!Time}

@@

We can instantiate \(\TS\) using a blockchain such as for instance OmniLedger~\cite{OmniLedger}.
The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and return the identifier of the block into which \(x\) was included.
\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted transactions and additional randomness (\eg nonces and miners' secrets).
The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
%Seb: why is the idea of using a dedicated blockchain not appropriate? we should give more arguments to justify it
Having a dedicated blockchain for a protest is not appropriate, and thus it is better to use a generic blockchain that is used also for other things.

There are some additional properties that we need from \(\TS\), which are implied by blockchains.
First, we need \emph{immutability}, to ensure that once we commit something (through \(\TSstamp\)) it will remain there.
Immutability will also ensure verifiability as the data must remain available to be verifiable.
Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
For instance in a blockchain, we can store the hash of the block in which our data was committed.
As a consequence as this block will remain, we are also sure that our data stay committed.% --- even if we no longer remember what our data looked like.

### 2018-06-01 paper/intro.tex

\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}) as well as a discussion of the performance and implementation issues (\cref{PerformanceAnalysis}). 
Finally, we conclude with a discussion and future works in \cref{Conclusion}.

>>>>

\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{RelatedWork}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 
Finally, we conclude with a discussion and future works in \cref{Conclusion}.
